Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Moreover, we write $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.

@@

\begin{definition}[Convex Elicitation Complexity]
	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ indirectly eliciting $\gamma$.
\end{definition}
In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$ when restricting to minimizable surrogates ($\Lcvx$).

>>>>

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
\raft{To discuss: add brief explanation for $\E_p$ notation, that $Y\sim p$?  Not sure if it's clear.}
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.

@@

\begin{definition}[Convex Elicitation Complexity]\label{def:cvx-elic-complex}
	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ indirectly eliciting $\gamma$.
\end{definition}
In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$ when restricting to minimizable surrogates ($\Lcvx$).
